Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/conclusions-and-future-work.tex
[ paper ] fixed a typo.
[ paper ] fixed conclusions.

We presented a reliable proof-reconstruction in type theory
for the propositional fragment of the \Metis prover. We provided for
each \Metis inference rule a formal description in type theory.
This formalizations is mainly exposed in
Section~\ref{ssec:emulating-inferences}.

>>>>

We presented a reliable proof-reconstruction in type theory
for the propositional fragment of the \Metis prover. We provided for
each \Metis inference rule a formal description in type theory
following a syntactical approach.
This formalizations are mainly exposed in
Section~\ref{ssec:emulating-inferences}.
